Price Tracing: Linking Nodal Prices in Optimized Power Systems

### 2022-03-16 submission-energy/paper/main.tex
finish submission to energy

    \begin{highlights}
        \item Flow Tracing is used to interlink optimal Locational Marginal Prices.
        \item This quantifies the payment of individual consumers to individual generators and transmission lines.
        \item Four use-cases are proposed and demonstrated on behalf of a future model of the German power system.
    \end{highlights}

    \begin{keyword}
        keywords here, in the form: keyword \sep keyword

        %% PACS codes here, in the form: \PACS code \sep code

        %% MSC codes here, in the form: \MSC code \sep code
        %% or \MSC[2008] code \sep code (2000 is the default)

>>>>

    \begin{highlights}
        \item Optimal Locational Marginal Prices are a direct result of a power system optimization. 
        \item Flow Tracing is used to interlink optimal Locational Marginal Prices.
        \item This quantifies the payment of individual consumers to individual generators and transmission lines.
        \item Four use-cases for improving transparency and fairness in the electricity market are proposed and demonstrated on behalf of a future model of the German power system.
    \end{highlights}

    \begin{keyword}

        Power System Optimization, Shadow Prices, Cost Allocation, Electricity Market, Power Flow Tracing
